---
title: "Crop Evapotranspiration"
author: "Allison Hacker"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(here)
source("ETc.R")
```

Crop evapotranspiration is important because it is indicative of how much water a crop requires. Crop ET is calculated using the Penman-Monteith equation and takes both climatic factors and crop-specific factors into account. This allows us to easily calculate the evapotranspiration for mulitple crops under a variety of different environmental conditions.

### Evapotranspiration based on wind speed
```{r, warning=FALSE}
nsample <- 100
wind_speeds <- rnorm(mean = 6, sd = 2, n = nsample)
ETc_norm <- data.frame(wind_speed = wind_speeds, ETc = NA)
ETc_norm$ETc = ETc(wind_speeds, 1.2)

ggplot(data = ETc_norm, aes(x = wind_speeds, y = ETc))+
  geom_point()+
  theme_bw()
```

### Evapotranspiration based on crop coefficient 

```{r}
nsample <- 100
crop_coeffs <- runif(nsample, min = 0.2, max = 2)
ETc_unif <- data.frame(crop_coeff = crop_coeffs, ETc = NA)
ETc_unif$ETc = ETc(6, crop_coeffs)

ggplot(data = ETc_unif, aes(x = crop_coeffs, y = ETc))+
  geom_point()+
  theme_bw()
```
The graphs show that crop evapotranspiration increases as wind speed increases. Evapotranspiration is also higher for crops that have a greater crop coefficient (Kc).
